Automated Verification for Real-Time Systems using Implicit Clocks and an Extended Antimirov Algorithm

### 2022-04-11 paper/tv.tex
m

\newcommand{\es}{\theta}
\newcommand{\ev}{ev}

@@

Specification and verification of real-time systems are important 
research topics which have practical implications. During the last 
more than two decades, a popular approach for specifying real-time systems is 
based on Timed Automata \cite{DBLP:journals/tcs/AlurD94}. 
Timed Automata are powerful 
in designing real-time models with explicit clock variables. Real-time 
constraints are captured by explicitly setting/reseting clock variables. 
A number of automatic verification support for Timed Automata have proven 
to be successful \cite{DBLP:journals/sttt/LarsenPY97,yovine1997kronos,wang2005verifying}.

Models based on Timed Automata often adapt a simple structure, e.g. a 
network with no hierarchy. The benefit is that 
efficient model checking is made feasible. Nonetheless, designing and 
verifying compositional real-time systems is becoming an increasingly 
difficult task due to the widespread applications and increasing complexity 
of such systems. In industrial case studies of real-time system verification, system 
requirements are often structured into phases, which are then composed 
sequentially, in parallel and alternatively \cite{DBLP:conf/emsoft/LarsenMNS05}. 
Unlike timed process algebras, Timed Automata lack high-level 
compositional patterns for hierarchical design. As a result, users often 
need to manually cast those terms into a set of clock variables with 
carefully calculated clock constraints. The process is tedious and error-prone.

We investigate an alternative approach for modeling and verifying 
compositional real-time systems. In this work, 
we propose a novel temporal specification language, 
which enables a compositional verification via a  Hoare-style 
forward verifier and a term rewriting system (TRS). 
More specifically, we specify system behaviours in the form of 
{Timed Effects} (\timedEffects), which integrates the Kleene Algebra with dependent values and arithmetic constraints, 
%gaining the expressive power beyond finite-state machines; and (ii) introduces a new parallel operator 
to 
%capture the parallelism between event-triggered (sync) and  time-triggered (async) execution traces, 
provide real-time abstractions into traditional linear temporal logics. 
%Resource usages, provided by a \emph{dynamic ticks}\cite{von2017real}, incorporating the time-triggered (physical time) and event-triggered (logical time) execution loops. 
For example, one safety property, \textit{"The event \anyevent{Done} 
will be triggered no later than one time unit"}\footnote{Without loss of generality, 
we use integer values to represent time units in this 
paper, while it can bes extended to real numbers and other 
time measurement units.}, is expressed in \timedEffects\ as: 
\code{\effect \defeq \  0 {\leq} t {<}1, ({\_^\star} \cdot \anyevent{Done} ) \mysharp  t}.
%\begin{align*}
%&\end{align*}  
%The timed effects incorporates different kinds of existing temporal logics, such as linear-time temporal logic (LTL)
%and .
%which replaces temporal operators by time-constrained versions from 
Here, \code{\mysharp } is a novel operator specifying the \emph{real-time} 
constraints for the \emph{logical-time} sequences \cite{von2017real}; 
\code{\_} is a wildcard matching to any event; 
Kleene star \code{\star} denotes trace repetition.
The above formula \code{\effect} corresponds to `\code{\Diamond_{[0, 1)}\ }\anyevent{Done}' 
in metric temporal logic (MTL), reads \textit{"within one second, 
\anyevent{Done} finally happens"}. Moreover, the time bounds 
can be dependent on the program inputs. For example, as the program 
shown in \autoref{fig:Value_dependent_intro}, we mark the precondition and postcondition
using keywords \code{\emph{require}} and \code{\emph{ensure}} respectively.

\newcommand{\codem}[1]{{\code{\emph{#1}}}}

\begin{wrapfigure}{L}{0.39\columnwidth}
  \vspace{-2mm}
\begin{lstlisting}
void oneSugar() 
/*req: TRUE/\ (_^*).emp
  ens: t>1 /\ emp#t */ 
{ timeout ((), 1); }

void addSugar (int n) 
/*req: n>=0 /\ _^*
  ens: t>=n /\ Sugar#t */
{ if (n == 0) { 
      event ["Sugar"];} 
  else {
      oneSugar();
      addSugar (n-1);}} 
\end{lstlisting}
\vspace{-1mm}
\caption{Value-dependent specification.} 
\label{fig:Value_dependent_intro}
\vspace{-1mm}
\end{wrapfigure}

The function 
\code{\emph{addSugar}} is intended to takes a parameter \codem{n}, representing 
the portion of the sugar we need to add. When \codem{n} decreases to \codem{0}, 
it simply raises an event Sugar to mark the end of the process. 
Otherwise, it adds one portion of the sugar then recursively calls \code{\emph{addSugar}} with parameter \codem{n-1}. 
The use of statement \codem{timeout(e, d)} is standard, 
which sets a timer which executes code \codem{e} once the timer 
expires at time \codem{d}. 
Therefore, the time spent on adding one portion of the sugar is 
no less than 1 time unit.

The specifications of  \codem{addSugar(n)} indicates that the 
input  \code{n} is non-negative; the method 
generates a finite trace where Sugar takes a no less 
than \code{d} time units delay to finish. 
Although these examples are simple, they show the benefits of deploying 
value-dependent 
time bounds, which is beyond the capability of Timed Automata. Intuitively, if traditional Timed Automata define an 
\emph{exact} transition system, \timedEffects\ define 
a set (possibly infinite) of exact transition systems.

\begin{comment}
  we express, the effects of \code{addSugar(d)} as:
\begin{align*}
&\code{\effect^{send (d)} \defeq \  (0 {<} d {\leq}5 \wedge  0 {\leq} t {<} d),  ({\anyevent{Send} \mysharp  t)} \cdot \anyevent{Done}}.
\end{align*}  
effects of \code{addSugar(n)} as:
\code{(n{>}0  \wedge  t {\geq} n) : ({Sugar \mysharp  t)}}

@@

\begin{enumerate}
\item \textbf{The Timed Effects:} We define the syntax 
({\secref{subsec:Specification_language}}) and semantics 
({\secref{subsec:Specification_Semantics}}) of \timedEffects, to be the 
specification language, which captures the target programs' behaviours 
and non-trivial temporal properties.

@@

\begin{figure}[ht]
      \vspace{0mm}
\begin{lstlisting}[columns=fullflexible]
void addSugar(int n)
/* req n>0,  _^*.Cup 
   ens  t>=n, Sugar # t */
{ if n == 0 then event[Sugar] 
  else {
    timeout (oneSugar(), 1);
    addSugar (n-1);}}

void makeCoffee (int n)
/* req n>0, emp 
 ens  t<5/\t>=n/\t1<3, 
 Cup.(Sugar#t).(Coffee#t1).Done */
{ event[Cup];
  deadline (addSugar(n), 5);
  deadline (event[Coffee], 3);
  event[Done];}

@@

{
\begin{figure}[!ht]
    %  \vspace{-4mm}
     \begin{minipage}[c]{\columnwidth}
         \centering
         {\small
         \begin{enumerate}
\item \lstinline|void addSugar (int n) {| \textcolor{mGray}{\footnotesize \emph{(-- initialize the current effects state --)}} \\
     \textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addSugar(n)} =  n{\geq}0 \wedge  \_^\star \} }} 
      \siderule{\scriptsize[FV\text{-}Meth] } \\
     \item ~\qquad \lstinline|if (n == 0) {| \\
     \textcolor{darklavender}{\code{\{ n{=}0 \wedge  \_^\star \}  }} \siderule{\scriptsize [FV\text{-}If-Else]}
      \item ~\qquad~\qquad \lstinline|event ["Sugar"];} |  \\
     \textcolor{darklavender}{\code{\{n{=}0 \wedge  \_^\star \cdot Sugar\} }} \siderule{\scriptsize [FV\text{-}Event]}
     \item 
     ~\qquad \lstinline|else {| \\
     \textcolor{darklavender}{\code{\{ n  {\neq} 0\}  }} \siderule{\scriptsize [FV\text{-}If-Else]}
    \item 
     ~\qquad~\qquad \lstinline|timeout (oneSugar() , 1);| \\
     \textcolor{darklavender}{\code{\{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t  }\}} \siderule {\scriptsize [FV\text{-}Event]}
     \item 
     ~\qquad~\qquad \lstinline|addSugar (n-1);}}|  \\
     \textcolor{huntergreen}{\code{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t   \CONTAIN \effect_{pre}^{addSugar(n\text{-}1)} }}
      \textcolor{mGray}{  \emph{(-check precondition-) }}\\
     \textcolor{darklavender}{\code{\{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star 
     \cdot \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)} }\}} 
     \siderule {\scriptsize [FV\text{-}Call]}
      \item \textcolor{darklavender}{\code{\effect_C^\prime {=} (n{=}0 \wedge  \_^\star \cdot Sugar)\ \vee\ }
      \code{ (n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)} ) }}
      \\
       \item 
       \textcolor{darkred}{\code{
       %\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{addSugar(n-1)}) } 
       \effect_C^\prime \CONTAIN \effect_{pre}^{addSugar(n)} \cdot \effect_{post}^{addSugar(n)} \Leftrightarrow  }}
        \textcolor{mGray}{  \emph{(-- check postcondition --) }}
        \\ 
        \textcolor{darkred}{\code{\code{\code{(n{=}0 \wedge Sugar)\ \vee\ }
        \code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)}) } \CONTAIN \effect_{post}^{addSugar(n)}}}}\\

@@

\Infer[dashed]1[{\siderule{\textcircled{1}[RENAME]}}]{\code{(n{=}0 \wedge Sugar)\ \vee\ }
\code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addSugar(n\text{-}1)}) } 
\CONTAIN \effect_{post}^{addSugar(n)}  }
\end{prooftree}}
\\~\\

@@

   \code{ \bott
   \  | \ \empt 
    \ | \ \ev
   \  | \ \es_1 {\seq} \es_2
    \ | \ \es_1 {\vee} \es_2
    \ | \ \es_1 {||} \es_2
    \ | \ \pi ?  \es
      %    \  | \ \es_1 \times \es_2
      \ | \ \es \mysharp  t 
   \  | \  \es^\star
}

@@

As the examples show, our proposed effects logic and the abstract semantics for \code{\timedL} not only tightly capture the behaviours of a mixed synchronous and asynchronous concurrency model but also help to mitigate the programming challenges in each paradigm. Meanwhile, the inferred temporal traces from a given reactive program enable a compositional timed temporal verification at the source level, which is not yet supported by existing temporal verification techniques.

@@

Moreover, this paper draws similarities to \textit{contextual effects} \cite{neamtiu2008contextual}, which computes the effects that have already occurred as the prior effects. The effects of the computation yet to take place as the future effects. 
Besides, prior work \cite{nielson1998behaviour} proposes an annotated type and effect system and infers behaviours from CML \cite{reppy1993concurrent} programs for channel-based communications, though it did not provide any inclusion solving process.

@@

\section{Conclusion}
\label{sec:conclusion}
%HipHop.js
We define the syntax and semantics of the novel \timedEffects, to capture reactive program behaviours and  temporal properties. We demonstrate how to give a rather axiomatic semantics to \code{\timedL} by timed-trace processing functions. We use this semantic model to enable  a Hoare-style forward verifier,  which computes the program effects constructively.
We present an effects inclusion checker (the TRS) to prove the annotated temporal properties efficiently. We prototype the verification system and show its feasibility.
To the best of our knowledge, our work is the first that formulates semantics of a mixed Sync-Async concurrency paradigm; and that automates modular timed verification for reactive programs using an expressive effects logic.

>>>>

\newcommand{\es}{\theta}
\newcommand{\ev}{ev}
\newcommand{\codem}[1]{{\lstinline[basicstyle=\small\ttfamily]|#1|}}

@@

Specification and verification of real-time systems are essential 
to research topics with practical implications. During the last 
more than two decades, a popular approach for specifying real-time systems has been 
based on Timed Automata \cite{DBLP:journals/tcs/AlurD94}. 
Timed Automata are powerful 
in designing real-time models with explicit clock variables. Real-time 
constraints are captured by explicitly setting/resetting clock variables. 
A number of automatic verification support for Timed Automata have proven 
to be successful \cite{DBLP:journals/tse/WangSWQ17,DBLP:journals/sttt/LarsenPY97,yovine1997kronos,wang2005verifying}.

Models based on Timed Automata often adopt a simple structure, e.g., a 
network with no hierarchy. The benefit is that 
efficient model checking is made feasible. Nonetheless, designing and 
verifying compositional real-time systems is becoming an increasingly 
difficult task due to the widespread applications and increasing complexity 
of such systems. In industrial case studies of real-time system verification, system 
requirements are often structured into phases, which are then composed 
sequentially, in parallel and alternatively \cite{DBLP:conf/emsoft/LarsenMNS05}. 
Unlike timed process algebras, Timed Automata lack high-level 
compositional patterns for hierarchical design. As a result, users often 
need to manually cast those terms into a set of clock variables with 
carefully calculated clock constraints. The process is tedious and error-prone.

We investigate an alternative approach for modeling and verifying 
compositional real-time systems. In this work, 
we propose a novel temporal specification language, 
which enables a compositional verification via a  Hoare-style 
forward verifier and a term rewriting system (TRS). 
More specifically, we specify system behaviors in the form of 
{Timed Effects} (\timedEffects), which integrates the Kleene Algebra 
with dependent values and arithmetic constraints, 
%gaining the expressive power beyond finite-state machines; and (ii) introduces a new parallel operator 
to 
%capture the parallelism between event-triggered (sync) and  time-triggered (async) execution traces, 
provide real-time abstractions into traditional linear temporal logics. 
%Resource usages, provided by a \emph{dynamic ticks}\cite{von2017real}, incorporating the time-triggered (physical time) and event-triggered (logical time) execution loops. 
For example, one safety property, \textit{"The event \anyevent{Done} 
will be triggered no later than one time unit"}\footnote{Without loss of generality, 
we use integer values to represent time units in this 
paper.% while it can bes extended to real numbers and other 
%time measurement units.
}, is expressed in \timedEffects\ as: 
\begin{align*}
  \code{\effect \defeq \  0 {\leq} t {<}1 \wedge ({\_^\star} \cdot \anyevent{Done} ) \mysharp  t}
\end{align*}  
%The timed effects incorporates different kinds of existing temporal logics, such as linear-time temporal logic (LTL)
%and .
%which replaces temporal operators by time-constrained versions from 
Here, \code{\wedge} connects the arithmetic formula and the timed trace, \code{\mysharp } is a novel operator specifying the \emph{real-time} 
constraints for the \emph{logical-time} sequences \cite{von2017real}; 
\code{\_} is a wildcard matching to any event; 
Kleene star \code{\star} denotes trace repetition.
The above formula \code{\effect} corresponds to `\code{\Diamond_{[0, 1)}\ }\anyevent{Done}' 
in metric temporal logic (MTL), reads \textit{"within one second, 
\anyevent{Done} finally happens"}.

Moreover, the time bounds 
can be dependent on the program inputs, demonstrated in \autoref{fig:Value_dependent_intro}, we mark the precondition and postcondition
using keywords {\color{darklavender}\code{\emph{req:}}} and {\color{darklavender}\code{\emph{ens:}}} respectively.

\begin{wrapfigure}{L}{0.39\columnwidth}
  \vspace{-2mm}
\begin{lstlisting}
void addOneSugar() 
/*req: TRUE/\ _^*
  ens: t>1 /\ emp#t */ 
{ timeout ((), 1); }

void addNSugar (int n) 
/*req: n>=0 /\ _^*
  ens: d>=n /\ Sugar#d */
{ if (n == 0) { 
      event ["Sugar"];} 
  else {
      addOneSugar();
      addNSugar (n-1);}} 
\end{lstlisting}
\vspace{-1mm}
\caption{Value-dependent specification.} 
\label{fig:Value_dependent_intro}
\vspace{-1mm}
\end{wrapfigure}

The function \codem{addNSugar} takes a parameter \codem{n}, representing 
the portion of the sugar we need to add. When \codem{n} 
equals to \codem{0}, 
it simply raises an event \anyevent{Sugar} to mark the end of the process. 
Otherwise, it adds one portion of the sugar by calling
\codem{addOneSugar()}, then recursively calls 
\codem{addNSugar} with parameter \codem{n-1}. 
The use of statement \lstinline|timeout(e, d)| is standard \cite{JSTO}, 
which executes a block of code \codem{e} after the specified time \codem{d}.
Therefore, the time spent on adding one portion of the sugar is 
no less than one time unit. Note that {\color{darklavender}\code{\emph{emp\#t}}} 
refers to an empty trace which takes time \codem{t}.

Both preconditions of \codem{addNSugar(n)} requies the 
input  \codem{n} is non-negative, and has no temporal constrains upon 
the history traces. 
The postcondition of \codem{addNSugar(n)} indicates that  the method 
generates a finite trace where \anyevent{Sugar} takes a no 
less 
than \codem{d} time-units delay to finish.

Although these examples are simple, they show the benefits of deploying 
value-dependent 
time bounds, which is beyond the capability of Timed Automata. Intuitively, if traditional Timed Automata define an 
\emph{exact} transition system, \timedEffects\ define 
a set (possibly infinite) of exact transition systems.

\begin{comment}
  we express, the effects of \code{addNSugar(d)} as:
\begin{align*}
&\code{\effect^{send (d)} \defeq \  (0 {<} d {\leq}5 \wedge  0 {\leq} t {<} d),  ({\anyevent{Send} \mysharp  t)} \cdot \anyevent{Done}}.
\end{align*}  
effects of \code{addNSugar(n)} as:
\code{(n{>}0  \wedge  t {\geq} n) : ({Sugar \mysharp  t)}}

@@

\begin{enumerate}
\item \textbf{The Timed Effects:} We define the syntax 
({\secref{subsec:Specification_language}}) and semantics 
({\secref{subsec:Specification_Semantics}}) of \timedEffects, to be the 
specification language, which captures the target programs' behaviors 
and non-trivial temporal properties.

@@

\begin{figure}[ht]
      \vspace{0mm}
\begin{lstlisting}[columns=fullflexible]
void addNSugar(int n)
/* req n>0,  _^*.Cup 
   ens  t>=n, Sugar # t */
{ if n == 0 then event[Sugar] 
  else {
    timeout ( addOneSugar(), 1);
    addNSugar (n-1);}}

void makeCoffee (int n)
/* req n>0, emp 
 ens  t<5/\t>=n/\t1<3, 
 Cup.(Sugar#t).(Coffee#t1).Done */
{ event[Cup];
  deadline (addNSugar(n), 5);
  deadline (event[Coffee], 3);
  event[Done];}

@@

{
\begin{figure}[!ht]
    %  \vspace{-4mm}
     \begin{minipage}[c]{\columnwidth}
         \centering
         {\small
         \begin{enumerate}
\item \lstinline|void addNSugar (int n) {| \textcolor{mGray}{\footnotesize \emph{(-- initialize the current effects state --)}} \\
     \textcolor{darklavender}{\{\code{\effect_C {=}\effect_{pre}^{addNSugar(n)} =  n{\geq}0 \wedge  \_^\star \} }} 
      \siderule{\scriptsize[FV\text{-}Meth] } \\
     \item ~\qquad \lstinline|if (n == 0) {| \\
     \textcolor{darklavender}{\code{\{ n{=}0 \wedge  \_^\star \}  }} \siderule{\scriptsize [FV\text{-}If-Else]}
      \item ~\qquad~\qquad \lstinline|event ["Sugar"];} |  \\
     \textcolor{darklavender}{\code{\{n{=}0 \wedge  \_^\star \cdot Sugar\} }} \siderule{\scriptsize [FV\text{-}Event]}
     \item 
     ~\qquad \lstinline|else {| \\
     \textcolor{darklavender}{\code{\{ n  {\neq} 0\}  }} \siderule{\scriptsize [FV\text{-}If-Else]}
    \item 
     ~\qquad~\qquad \lstinline|timeout ( addOneSugar() , 1);| \\
     \textcolor{darklavender}{\code{\{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t  }\}} \siderule {\scriptsize [FV\text{-}Event]}
     \item 
     ~\qquad~\qquad \lstinline|addNSugar (n-1);}}|  \\
     \textcolor{huntergreen}{\code{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t   \CONTAIN \effect_{pre}^{addNSugar(n\text{-}1)} }}
      \textcolor{mGray}{  \emph{(-check precondition-) }}\\
     \textcolor{darklavender}{\code{\{n  {\neq} 0  \wedge t{>}1  \wedge \_^\star 
     \cdot \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)} }\}} 
     \siderule {\scriptsize [FV\text{-}Call]}
      \item \textcolor{darklavender}{\code{\effect_C^\prime {=} (n{=}0 \wedge  \_^\star \cdot Sugar)\ \vee\ }
      \code{ (n  {\neq} 0  \wedge t{>}1  \wedge \_^\star \cdot \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)} ) }}
      \\
       \item 
       \textcolor{darkred}{\code{
       %\code{(n{=}0 \wedge \anyevent{Done})\ \vee\ }\code{ (n  \neq 0  \wedge \anyevent{Send}\cdot \effect_{post}^{addNSugar(n-1)}) } 
       \effect_C^\prime \CONTAIN \effect_{pre}^{addNSugar(n)} \cdot \effect_{post}^{addNSugar(n)} \Leftrightarrow  }}
        \textcolor{mGray}{  \emph{(-- check postcondition --) }}
        \\ 
        \textcolor{darkred}{\code{\code{\code{(n{=}0 \wedge Sugar)\ \vee\ }
        \code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)}) } \CONTAIN \effect_{post}^{addNSugar(n)}}}}\\

@@

\Infer[dashed]1[{\siderule{\textcircled{1}[RENAME]}}]{\code{(n{=}0 \wedge Sugar)\ \vee\ }
\code{ (n  {\neq} 0  \wedge  t{>}1  \wedge \epsilon \mysharp t \cdot \effect_{post}^{addNSugar(n\text{-}1)}) } 
\CONTAIN \effect_{post}^{addNSugar(n)}  }
\end{prooftree}}
\\~\\

@@

   \code{ \bott
   \  | \ \empt 
    \ | \ \ev
   \  | \ \es_1 {\seq} \es_2
    \ | \ \es_1 {\vee} \es_2
    \ | \ \es_1 {||} \es_2
    \ | \ \pi ? 
      %    \  | \ \es_1 \times \es_2
      \ | \ \es \mysharp  t 
   \  | \  \es^\star
}

@@

As the examples show, our proposed effects logic and the abstract semantics for \code{\timedL} not only tightly capture the behaviors of a mixed synchronous and asynchronous concurrency model but also help to mitigate the programming challenges in each paradigm. Meanwhile, the inferred temporal traces from a given reactive program enable a compositional timed temporal verification at the source level, which is not yet supported by existing temporal verification techniques.

@@

Moreover, this paper draws similarities to \textit{contextual effects} \cite{neamtiu2008contextual}, which computes the effects that have already occurred as the prior effects. The effects of the computation yet to take place as the future effects. 
Besides, prior work \cite{nielson1998behaviour} proposes an annotated type and effect system and infers behaviors from CML \cite{reppy1993concurrent} programs for channel-based communications, though it did not provide any inclusion solving process.

@@

\section{Conclusion}
\label{sec:conclusion}
%HipHop.js
We define the syntax and semantics of the novel \timedEffects, to capture reactive program behaviors and  temporal properties. We demonstrate how to give a rather axiomatic semantics to \code{\timedL} by timed-trace processing functions. We use this semantic model to enable  a Hoare-style forward verifier,  which computes the program effects constructively.
We present an effects inclusion checker (the TRS) to prove the annotated temporal properties efficiently. We prototype the verification system and show its feasibility.
To the best of our knowledge, our work is the first that formulates semantics of a mixed Sync-Async concurrency paradigm; and that automates modular timed verification for reactive programs using an expressive effects logic.
